Supplementary Figures---``\emph{scater:} pre-processing, quality control, normalisation and visualisation of single-cell RNA-seq data in R''

### 2016-08-14 supplement_figs.tex
scater paper ready for submission

\title[scater supplementary figures]{Supplementary Figures---``\emph{scater:} pre-processing, quality control, normalisation and visualisation of single-cell RNA-seq data in R''}
\author{Davis J.~McCarthy\,$^{\text{1,2,4,6}*}$, Kieran R.~Campbell\,$^{\text{2,5}}$, Aaron T.~L.~Lun\,$^{\text{7}}$ and Quin F.~Wills\,$^{\text{2,3}}$}
\address{$^{\text{1}}$European Molecular Biology Laboratory - European Bioinformatics Institute (EMBL-EBI), Hinxton CB10 1SD, Cambridgeshire, UK;\\
$^{\text{2}}$Wellcome Trust Centre for Human Genetics, University of Oxford,
Oxford, Oxfordshire, UK;\\
$^{\text{3}}$ Weatherall Institute for Molecular Medicine, University of Oxford, Oxford, Oxfordshire, UK;\\
$^{\text{4}}$Department of Statistics, University of Oxford, Oxford, Oxfordshire, UK;\\
$^{\text{5}}$Department of Anatomy, Physiology and Genetics, University of Oxford, Oxford, Oxfordshire, UK;\\
$^{\text{6}}$St Vincent's Institute of Medical Research, 41 Victoria Parade Fitzroy Victoria 3065, Australia; and \\
$^{\text{7}}$CRUK Cambridge Institute, Robinson Way, Cambridge CB2 0RE,
Cambridgeshire, UK.}

\begin{abstract}
Supplementary Figures---an overview of the SCESet class; an overview of the \emph{scater} ecosystem; examples of using the \emph{scater} GUI.\\ \\
\textbf{Contact:} \href{davis@ebi.ac.uk}{davis@ebi.ac.uk}
\end{abstract}

@@

>>>>

\title[scater supplementary figures]{Supplementary Figures---``\emph{scater:} pre-processing, quality control, normalisation and visualisation of single-cell RNA-seq data in R''}
\author{Davis J.~McCarthy\,$^{\text{1,2,5}*}$, Kieran R.~Campbell\,$^{\text{2,4}}$, Aaron T.~L.~Lun\,$^{\text{6}}$ and Quin F.~Wills\,$^{\text{2,3}}$}
\address{$^{\text{1}}$European Molecular Biology Laboratory - European Bioinformatics Institute (EMBL-EBI), Hinxton CB10 1SD, United Kingdom;\\
$^{\text{2}}$Wellcome Trust Centre for Human Genetics, University of Oxford,
Roosevelt Drive, Oxford OX3 7BN, United Kingdom;\\
$^{\text{3}}$Weatherall Institute for Molecular Medicine, University of Oxford, John Radcliffe Hospital, Oxford OX3 9DS, United Kingdom;\\
$^{\text{4}}$Department of Physiology, Anatomy and Genetics, University of Oxford, South Parks Road, Oxford OX1 3QX, United Kingdom;\\
$^{\text{5}}$St Vincent's Institute of Medical Research, 41 Victoria Parade, Fitzroy Victoria 3065, Australia; and \\
$^{\text{6}}$CRUK Cambridge Institute, University of Cambridge, Robinson Way, Cambridge CB2 0RE, United Kingdom.
% $^{\text{\sf 4}}$Department of Statistics, University of Oxford, Oxford, Oxfordshire, UK;
}

\begin{abstract}
Supplementary material and figures---details of package dependencies; an overview of the SCESet class; an overview of the \emph{scater} ecosystem; examples of using the \emph{scater} GUI.\\ \\
\textbf{Contact:} \href{davis@ebi.ac.uk}{davis@ebi.ac.uk}
\end{abstract}

@@

\begin{figure}[!tpb]
\centerline{\includegraphics[width=0.7\textwidth]{figures/find-pcs_c1_machine.pdf}}
\caption{A QC plot produced by the plotQC function in \emph{scater} showing violin, scatter- and boxplots of principal component values against the C1 machine used for each cell for the six principal components most strongly correlated with C1 machine used.}\label{fig:plotqc-c1-machine}
\end{figure}
